Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_review.Rmd
revising results with final results

*Background.* Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate by their impact  on the global carbon (C) cycle. However, efforts to incorporate forests into climate models and CO2 accounting frameworks have been constrained by a lack of accessible, global-scale data on how C cycling varies across forest types and stand ages.

@@

**check this with final data (based on Table 1):**
There were sufficient data to assess mature forest biome differences for **9** stock variables, and significant differences among biomes were detected for **6** variables (**$B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$, $DW_{tot}$**; Table 1).
C stocks had less consistent patterns across biomes (Figs. 7, S16-S26).
In **four of the six** cases (**$B_{tot}$, $B_{ag-wood}$,  $B_{root-coarse}$, $DW_{tot}$**), temperate conifer forests had significantly higher stocks than the other biomes, and boreal forests in the lowest, with tropical and temperate broadleaf forests in between.
For $B_{ag}$, which had by far the highest sample size, tropical forests exceeded temperate conifer forests (but not significantly). 
For $B_{foliage}$,temperate broadleaf forests were lowest (again, not significantly).
The high values for the temperate conifer biome were driven by the very high-biomass forests of the US Pacific Northwest, which are disproportionately represented in the current version of ForC.
Thus, biome differences should be interpreted more as driven more by geographic distribution of sampling than by true differences.

@@

Average C cycles for forests <100 years old are presented in Figures 8-11.  
Both C stocks and fluxes commonly increased signficantly with stand age (Tables 1, S2, Figs. 6-11, S1-S26; detailed below).

>>>>

*Background.* Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate by their impact  on the global carbon (C) cycle. However, efforts to incorporate forests into climate models and CO~2~ accounting frameworks have been constrained by a lack of accessible, global-scale data on how C cycling varies across forest types and stand ages.

@@

There were sufficient data to assess mature forest biome differences for nine stock variables, and significant differences among biomes were detected for five variables ($B_{tot}$, $B_{ag}$, $B_{ag-wood}$, $B_{foliage}$, $B_{root-coarse}$; Table 1).
C stocks had less consistent patterns across biomes (Figs. 7, S16-S26).
For $B_{tot}$ and $B_{ag}$, tropical broadleaf forests had the highest biomass and boreal forests the lowest, with temperate broadleaf and needleleaf ($B_{ag}$ only) intermediate.
For three variables that had been disproportionately sampled in the high-biomass forests of the US Pacific Northwest ($B_{ag-wood}$, $B_{foliage}$, and $B_{root-coarse}$), temperate conifer forests had significantly higher stocks than the other biomes, which were not significantly different from one another.

@@

Average C cycles for forests <100 years old are presented in Figures 8-11.  
Both C stocks and fluxes commonly increased significantly with stand age (Tables 1, S2, Figs. 6-11, S1-S26; detailed below).
